---
title: "OLTP_CPU_TEST"
output:
  html_document:
    toc: true
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(jsonlite)
library(data.table)
library(tidyverse)
library(ggplot2)
library(rjson)
library(rlist)
library(future)
library(furrr)
library(parallel)
library(foreach)
library(doParallel)
library(tictoc)
library(plotly)
require(magick)
require(cowplot)
library(lubridate)
library(fst)
library(scales)
library(patchwork)

options(digits.secs = 3)  
options(scipen = 999)

source("00_functions.R")
source("00_viz_functions.R")
```


```{r, read_the_data, results='asis', echo=FALSE, message = FALSE, echo = FALSE, warning=FALSE}

curent_dir <- system("pwd",intern = TRUE)
path_to_file <- paste(curent_dir,"oltp_sysbench_logs.fst", sep="/")
oltp_test_result <- fst::read.fst(path_to_file) %>% as.data.table()
```




# Auto generated report and pictures

## Talbe with results
```{R, datatable, results='asis', echo=FALSE, message = FALSE, echo = FALSE, warning=FALSE}
# knitr::kable(oltp_test_result, caption = "EC2 summary")
DT::datatable(oltp_test_result, 
              class = 'cell-border stripe',
              caption = 'Table 1: Raw results for the experiment',
              extensions = "Buttons", 
            options = list(paging = TRUE,
                           scrollX=TRUE, 
                           searching = TRUE,
                           ordering = TRUE,
                           dom = 'Bfrtip',
                           buttons = c('copy', 'csv', 'excel'),
                           pageLength=5, 
                           lengthMenu=c(3,5,10) ))
```




## Manual prepared graphs


### THROUGHPUT (QURIES PER SECOND)
```{R, manual_plots_QPS,results='asis', out.extra='style="background-color: #9ecff7; padding:10px; display: inline-block;"',  echo=FALSE,                                                                                 message = FALSE, echo = FALSE, warning=FALSE, fig.width=unit(16,"cm"), fig.height=unit(10,"cm"), out.width = "100%" }
p_03 <- get_db_universal(oltp_test_result,
                         input_title = "Queries per second",
                         column_name = "queries_per_sec",
                         yaxis_label = "Amount of queries per second",
                         input_subtitle = "( more is better )",
                         input_caption = "sysbench: 1.0.18, MySQL: 8.0.26-0",
                         x_axis_aws = FALSE,
                         add_logo = TRUE,
                         facet_cpu=TRUE)
# 
print(p_03)
```

#### Queries per second details
<details><summary style='background-color: #EEEEEE;color: #333333; padding: 2px 6px 2px 6px; border-top: 1px solid #CCCCCC; border-right: 1px solid #333333; border-bottom: 1px solid #333333; border-left: 1px solid #CCCCCC;'>Details:  Queries per second details</summary>

```{r queries_per_second_details, results='asis', out.extra='style="background-color: #9ecff7; padding:10px; display: inline-block;"',  echo=FALSE,                                                                                 message = FALSE, echo = FALSE, warning=FALSE, fig.width=unit(16,"cm"), fig.height=unit(10,"cm"), out.width = "100%"} 
p_02_s <- get_db_universal(oltp_test_result[ec2_type == "small"],
                           input_title = "Queries per second (vCPU: 2, 4,8)",
                           column_name = "queries_per_sec",
                           yaxis_label = "Amount of queries per second",
                           input_subtitle = "( more is better )",
                           input_caption = "sysbench: 1.0.18, MySQL: 8.0.26-0",
                           x_axis_aws = FALSE,
                           add_logo = TRUE,
                           facet_cpu=TRUE)

print(p_02_s)


p_02_m <- get_db_universal(oltp_test_result[ec2_type == "medium"],
                           input_title = "Queries per second (vCPU: 16, 32)",
                           column_name = "queries_per_sec",
                           yaxis_label = "Amount of queries per second",
                           input_subtitle = "( more is better )",
                           input_caption = "sysbench: 1.0.18, MySQL: 8.0.26-0",
                           x_axis_aws = FALSE,
                           add_logo = TRUE,
                           facet_cpu=TRUE)

print(p_02_m)


p_02_f <- get_db_universal(oltp_test_result[ec2_type == "large"],
                           input_title = "Queries per second (vCPU: 48, 64)",
                           column_name = "queries_per_sec",
                           yaxis_label = "Amount of queries per second",
                           input_subtitle = "( more is better )",
                           input_caption = "sysbench: 1.0.18, MySQL: 8.0.26-0",
                           x_axis_aws = FALSE,
                           add_logo = TRUE,
                           facet_cpu=TRUE)
print(p_02_f)
```
</details>



### LATENCIES (95th Percentile)
```{R, manual_plots_latencies,results='asis', out.extra='style="background-color: #9ecff7; padding:10px; display: inline-block;"',  echo=FALSE,                                                                                 message = FALSE, echo = FALSE, warning=FALSE, fig.width=unit(16,"cm"), fig.height=unit(10,"cm"), out.width = "100%" }
p95_O <- get_db_universal(oltp_test_result,
                        input_title = "Latency (95th percentile) during test",
                        column_name = "latency_ms_95th_percentile",
                        input_subtitle = "( less is better )",
                        input_caption = "sysbench: 1.0.18, MySQL: 8.0.26-0",
                        yaxis_label = "Latency 95 percentile (ms)",
                        x_axis_aws = FALSE,
                        add_logo = TRUE,
                        facet_cpu=TRUE)
print(p95_O)
```

 
#### latencies details
<details><summary style='background-color: #EEEEEE;color: #333333; padding: 2px 6px 2px 6px; border-top: 1px solid #CCCCCC; border-right: 1px solid #333333; border-bottom: 1px solid #333333; border-left: 1px solid #CCCCCC;'>Details:  Latencies details</summary>

```{r Latencies_details, results='asis', out.extra='style="background-color: #9ecff7; padding:10px; display: inline-block;"',  echo=FALSE,                                                                                 message = FALSE, echo = FALSE, warning=FALSE, fig.width=unit(16,"cm"), fig.height=unit(10,"cm"), out.width = "100%"} 

p95_s <- get_db_universal(oltp_test_result[ec2_type == "small"],
                        input_title = "Latency (95th percentile) during test",
                        column_name = "latency_ms_95th_percentile",
                        input_subtitle = "( less is better )",
                        input_caption = "sysbench: 1.0.18, MySQL: 8.0.26-0",
                        yaxis_label = "Latency 95 percentile (ms)",
                        x_axis_aws = FALSE,
                        add_logo = TRUE,
                        facet_cpu=TRUE)
print(p95_s)


p95_m <- get_db_universal(oltp_test_result[ec2_type == "medium"],
                        input_title = "Latency (95th percentile) during test",
                        column_name = "latency_ms_95th_percentile",
                        input_subtitle = "( less is better )",
                        input_caption = "sysbench: 1.0.18, MySQL: 8.0.26-0",
                        yaxis_label = "Latency 95 percentile (ms)",
                        x_axis_aws = FALSE,
                        add_logo = TRUE,
                        facet_cpu=TRUE)
print(p95_m)


p95_f <- get_db_universal(oltp_test_result[ec2_type == "large"],
                        input_title = "Latency (95th percentile) during test",
                        column_name = "latency_ms_95th_percentile",
                        input_subtitle = "( less is better )",
                        input_caption = "sysbench: 1.0.18, MySQL: 8.0.26-0",
                        yaxis_label = "Latency 95 percentile (ms)",
                        x_axis_aws = FALSE,
                        add_logo = TRUE,
                        facet_cpu=TRUE)

print(p95_f)
```
</details>




### ABSOLUTE COMPARISON
```{R, manual_plots_absolute_comparison,results='asis', out.extra='style="background-color: #9ecff7; padding:10px; display: inline-block;"',  echo=FALSE,                                                                                 message = FALSE, echo = FALSE, warning=FALSE, fig.width=unit(16,"cm"), fig.height=unit(10,"cm"), out.width = "100%" }
abs_com_overview <- intel_graviton_comparison(oltp_test_result,
                                              input_subtitle="",
                                              input_caption= "sysbench: 1.0.18, MySQL: 8.0.26-0",
                                              input_relative=FALSE)
print(abs_com_overview)
```




#### Absolute comparison details
<details><summary style='background-color: #EEEEEE;color: #333333; padding: 2px 6px 2px 6px; border-top: 1px solid #CCCCCC; border-right: 1px solid #333333; border-bottom: 1px solid #333333; border-left: 1px solid #CCCCCC;'>Details:  Absolute comparison</summary>
```{r absolute_comparison_details, results='asis', out.extra='style="background-color: #9ecff7; padding:10px; display: inline-block;"',  echo=FALSE,                                                                                 message = FALSE, echo = FALSE, warning=FALSE, fig.width=unit(16,"cm"), fig.height=unit(10,"cm"), out.width = "100%"} 

abs_com_s <- intel_graviton_comparison(oltp_test_result[ec2_type == "small"],
                                       input_subtitle="",
                                       input_caption= "sysbench: 1.0.18, MySQL: 8.0.26-0",
                                       input_relative=FALSE)
print(abs_com_s)


abs_com_m <- intel_graviton_comparison(oltp_test_result[ec2_type == "medium"],
                                       input_subtitle="",
                                       input_caption= "sysbench: 1.0.18, MySQL: 8.0.26-0",
                                       input_relative=FALSE)
print(abs_com_m)


abs_com_f <- intel_graviton_comparison(oltp_test_result[ec2_type == "large"],
                                       input_subtitle="",
                                       input_caption= "sysbench: 1.0.18, MySQL: 8.0.26-0",
                                       input_relative=FALSE)
print(abs_com_f)


```
</details>





### RELATIVE COMPARISON
```{R, manual_plots_relative_comparison,results='asis', out.extra='style="background-color: #9ecff7; padding:10px; display: inline-block;"',  echo=FALSE,                                                                                 message = FALSE, echo = FALSE, warning=FALSE, fig.width=unit(16,"cm"), fig.height=unit(10,"cm"), out.width = "100%" }
rel_com_overview <- intel_graviton_comparison(oltp_test_result,
                                              input_subtitle="",
                                              input_caption= "sysbench: 1.0.18, MySQL: 8.0.26-0",
                                              input_relative=TRUE)
print(rel_com_overview)
```


#### Relative comparison details
<details><summary style='background-color: #EEEEEE;color: #333333; padding: 2px 6px 2px 6px; border-top: 1px solid #CCCCCC; border-right: 1px solid #333333; border-bottom: 1px solid #333333; border-left: 1px solid #CCCCCC;'>Details:  Relative comparison</summary>
```{r manual_plots_relative_comparison_details, results='asis', out.extra='style="background-color: #9ecff7; padding:10px; display: inline-block;"',  echo=FALSE,                                                                                 message = FALSE, echo = FALSE, warning=FALSE, fig.width=unit(16,"cm"), fig.height=unit(10,"cm"), out.width = "100%"} 


rel_com_s <- intel_graviton_comparison(oltp_test_result[ec2_type == "small"],
                                              input_subtitle="",
                                              input_caption= "sysbench: 1.0.18, MySQL: 8.0.26-0",
                                              input_relative=TRUE)
print(rel_com_s)


rel_com_m <- intel_graviton_comparison(oltp_test_result[ec2_type == "medium"],
                                              input_subtitle="",
                                              input_caption= "sysbench: 1.0.18, MySQL: 8.0.26-0",
                                              input_relative=TRUE)
print(rel_com_m)


rel_com_f <- intel_graviton_comparison(oltp_test_result[ec2_type == "large"],
                                              input_subtitle="",
                                              input_caption= "sysbench: 1.0.18, MySQL: 8.0.26-0",
                                              input_relative=TRUE)
print(rel_com_f)

```
</details>




### REQUEST PER DOLLAR
```{R, manual_plots_RPD,results='asis', out.extra='style="background-color: #9ecff7; padding:10px; display: inline-block;"',  echo=FALSE,                                                                                 message = FALSE, echo = FALSE, warning=FALSE, fig.width=unit(16,"cm"), fig.height=unit(10,"cm"), out.width = "100%" }
p_05_rpd_overview <- requests_per_dollar(oltp_test_result)
print(p_05_rpd_overview)
```


#### Request per dollar details
<details><summary style='background-color: #EEEEEE;color: #333333; padding: 2px 6px 2px 6px; border-top: 1px solid #CCCCCC; border-right: 1px solid #333333; border-bottom: 1px solid #333333; border-left: 1px solid #CCCCCC;'>Details:  Request per dollar</summary>
```{r RPD_details, results='asis', out.extra='style="background-color: #9ecff7; padding:10px; display: inline-block;"',  echo=FALSE,                                                                                 message = FALSE, echo = FALSE, warning=FALSE, fig.width=unit(16,"cm"), fig.height=unit(10,"cm"), out.width = "100%"} 

# save_plot("05_p_05_rpd_overview.png", p_05_rpd_overview)
p_05_rpd_s <- requests_per_dollar(oltp_test_result[ec2_type == "small"])
print(p_05_rpd_s)

p_05_rpd_m <- requests_per_dollar(oltp_test_result[ec2_type == "medium"])
print(p_05_rpd_m)

p_05_rpd_f <- requests_per_dollar(oltp_test_result[ec2_type == "large"])
print(p_05_rpd_f)


```
</details>




### REQUEST PER HOUR
```{R, manual_plots_RPH,results='asis', out.extra='style="background-color: #9ecff7; padding:10px; display: inline-block;"',  echo=FALSE,                                                                                 message = FALSE, echo = FALSE, warning=FALSE, fig.width=unit(16,"cm"), fig.height=unit(10,"cm"), out.width = "100%" }
p_06_rph_overview <- requests_ph(oltp_test_result)
print(p_06_rph_overview)
```


#### Request per hour details
<details><summary style='background-color: #EEEEEE;color: #333333; padding: 2px 6px 2px 6px; border-top: 1px solid #CCCCCC; border-right: 1px solid #333333; border-bottom: 1px solid #333333; border-left: 1px solid #CCCCCC;'>Details:  Request per hour</summary>
```{r RPH_details, results='asis', out.extra='style="background-color: #9ecff7; padding:10px; display: inline-block;"',  echo=FALSE,                                                                                 message = FALSE, echo = FALSE, warning=FALSE, fig.width=unit(16,"cm"), fig.height=unit(10,"cm"), out.width = "100%"} 



p_06_rph_s <- requests_ph(oltp_test_result[ec2_type == "small"])
print(p_06_rph_s)

p_06_rph_m <- requests_ph(oltp_test_result[ec2_type == "medium"])
print(p_06_rph_m)

p_06_rph_f <- requests_ph(oltp_test_result[ec2_type == "large"])
print(p_06_rph_f)



```
</details>


### EFFICIENCY OVERVIEW
```{R, manual_plots_efficiency,results='asis', out.extra='style="background-color: #9ecff7; padding:10px; display: inline-block;"',  echo=FALSE,                                                                                 message = FALSE, echo = FALSE, warning=FALSE, fig.width=unit(16,"cm"), fig.height=unit(10,"cm"), out.width = "100%" }
p_07_efficiency_overview <- efficient_comparison_point_plot(oltp_test_result, facet_threads=FALSE)
print(p_07_efficiency_overview)
```



## Autogenerated graphs

```{r, auto_gen_pics, results='asis', out.extra='style="background-color: #9ecff7; padding:10px; display: inline-block;"',  echo=FALSE,                                                                                 message = FALSE, echo = FALSE, warning=FALSE, fig.width=unit(16,"cm"), fig.height=unit(10,"cm"), out.width = "100%"}

col_list <- c("read" ,"query_exec_other",
              "query_exec_general_statistic_total_number_of_events","latency_ms_min", "latency_ms_avg", "latency_ms_max",
              "latency_ms_95th_percentile", "latency_ms_sum", "latency_ms_events_avg", "latency_ms_events_stddev",
              "latency_ms_execution_time_avg","latency_ms_execution_time_stddev", "sql_stat_transactions_total",
              "sql_stat_transactions_per_sec","queries_total", "queries_per_sec" )


cpuList <- oltp_test_result$cpu_amount %>% unique()
ec2_types <- oltp_test_result$ec2_type %>% unique()


for(column in col_list){
cat("\n")
cat("\n")
cat("<input type=\"button\" onclick=\"location.href='#top';\" value=\"Back to top\" />")
cat("\n")
cat("\n")

cat("### ","Section: ",  column, "\n")

  autogenerated_title <- paste(column,"autogenerated", sep = "_")

  auto_plot <- get_db_universal(oltp_test_result,
                           input_title = autogenerated_title,
                           column_name = column,
                           yaxis_label = column,
                           input_subtitle = "",
                           input_caption = "sysbench: 1.0.18, MySQL: 8.0.26-0",
                           x_axis_aws = FALSE,
                           add_logo = TRUE,
                           facet_cpu=TRUE)

  print(auto_plot)
  cat("\n")
  cat("\n")

  # cat("<details><summary style='background-color:#F1EC5E;font-size:35px;'>","more details: ", column, "</summary>")
  cat("<details><summary style='background-color: #EEEEEE;color: #333333; padding: 2px 6px 2px 6px; border-top: 1px solid #CCCCCC; border-right: 1px solid #333333; border-bottom: 1px solid #333333; border-left: 1px solid #CCCCCC;'>","more details: ", column, "</summary>")
  for(cpu_num in cpuList){
    autogenerated_title <- paste(column, "for", cpu_num,"cpu","autogenerated", sep = "_")

    auto_plot <- get_db_universal(oltp_test_result[cpu_amount == cpu_num],
                                  input_title = autogenerated_title,
                                  column_name = column,
                                  yaxis_label = column,
                                  input_subtitle = "",
                                  input_caption = "sysbench: 1.0.18, MySQL: 8.0.26-0",
                                  x_axis_aws = FALSE,
                                  add_logo = TRUE,
                                  facet_cpu=TRUE)

    print(auto_plot)
    cat("\n")
    cat("\n")
  }

  cat("</details>")
  cat("</details>")
  cat("\n")
  cat("\n")
  cat("<br>")
  cat("<br>")
  cat("<br>")
}

```


```{r percona_logo, echo=FALSE, fig.cap="build with Percona", out.width = '12%',style='background-color=#F1EC5E;font-size=10px;'}
knitr::include_graphics("https://avatars.githubusercontent.com/u/1683025?s=200&v=4")
```